Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-11 manuscript/manuscript.Rmd
Added data on fits for outlier example data.

The Top Gear dataset contains data on 297 vehicles that appeared on the BBC television show *Top Gear* [@Alfons2021-kc].
Within this dataset, the fuel consumption feature contains outliers due to highly fuel-efficient vehicles.

Applying conventional and invariant Yeo-Johnson transformations to the fuel consumption feature yielded the following results, see Figure \ref{fig:experimental-results-outlier-robustness}:
no transformation (residual sum $\sum r_i = 110$, $p=0.76$);
conventional transformation ($\lambda = -0.7$, $\sum r_i = 30$, $\mu_{YJ} = 1.0$, $\sigma_{YJ} = 0.1$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 1.1$, $\sum r_i = 137$, $\mu_{YJ} = 7.2$, $\sigma_{YJ} = 14$, $p=0.61$);
location- and scale-invariant transformation ($\lambda = 0.2$, $\sum r_i = 12$, $\mu_{YJ} = -11.8$, $\sigma_{YJ} = 6.9$, $p=0.13$);
and robust location- and scale-invariant transformation ($\lambda = -0.6$, $\sum r_i = 27$, $\mu_{YJ} = 0.7$, $\sigma_{YJ} = 0.1$, $p=0.10$).

>>>>

The Top Gear dataset contains data on 297 vehicles that appeared on the BBC television show *Top Gear* [@Alfons2021-kc].
Within this dataset, the fuel consumption feature contains outliers due to highly fuel-efficient vehicles.
Applying conventional and invariant Yeo-Johnson transformations to the fuel consumption feature yielded the following results, see Figure \ref{fig:experimental-results-outlier-robustness}:
no transformation (residual sum $\sum r_i = 54$, $p=0.56$);
conventional transformation ($\lambda = -0.1$, $\sum r_i = 55$, $\mu_{YJ} = 3.0$, $\sigma_{YJ} = 0.3$, $p=0.01$);
Raymaekers and Rousseeuw's robust adaptation ($\lambda = 0.8$, $\sum r_i = 48$, $\mu_{YJ} = 29$, $\sigma_{YJ} = 15$, $p=0.61$);
location- and scale-invariant transformation ($\lambda = -1.3$, $\sum r_i = 44$, $\mu_{YJ} = 0.5$, $\sigma_{YJ} = 0.1$, $p=0.13$);
and robust location- and scale-invariant transformation ($\lambda = -0.9$, $\sum r_i = 50$, $\mu_{YJ} = 2.0$, $\sigma_{YJ} = 2.3$, $p=0.10$).
